Usage metrics

### 2021-01-04 analysis/usage.Rmd
na.rm = TRUE for the opcode computations

```{r amount_computations, include=F}
tot_events <- E %>%
  summarise(n = sum(opcodes * duplicates)) %>%
  .$n
max_events <- E %>%
  summarize(n = max(opcodes)) %>%
  .$n

>>>>

```{r amount_computations, include=F}
tot_events <- E %>%
  summarise(n = sum(opcodes * duplicates, na.rm = TRUE)) %>%
  .$n
max_events <- E %>%
  summarize(n = max(opcodes, na.rm = TRUE)) %>%
  .$n
